### 2020-12-16 Thesis-Chapter6-ThreatModel.tex
Editorial improvements

\modelitem{Transparency}{The system should be auditable by the public to enable verification that its power is being
used responsibly. In the case of \ac{DAR}, the subject of the search should be aware of the access.}

@@

\modelitem{Foreign intelligence}{Foreign intelligence agencies and \acp{APT} are constantly looking for ways to escalate
privilege and tamper with or steal information. They have world-class expertise and computing power, which they can
apply to both individual devices and backend systems. (Here I am referring to \ii{foreign} foreign intelligence
agencies, as opposed to \ii{domestic} foreign intelligence agencies such as the \acs{CIA} or \acs{NSA} in the U.S.,
which are assumed to operate within---though push the boundaries of---the legal framework.)}

@@

Hawkish lawmakers threaten the security of a cryptosystem (using \ac{EA} or not) because they may judge the system as
too inhibitive to law enforcement. Therefore, they may outlaw its use and mandate something weaker in its place.}

>>>>

\modelitem{Transparency}{The system should be auditable by the public to allow for verification that its power is being
used responsibly. In the case of \ac{DAR}, the subject of the search should be aware of the access.}

@@

\modelitem{Foreign intelligence}{Foreign intelligence agencies and \acp{APT} are constantly looking for ways to escalate
their privilege and tamper with or steal information. They have world-class expertise and computing power, which they
can apply to both individual devices and backend systems. (Here I am referring to \ii{foreign} foreign intelligence
agencies, as opposed to \ii{domestic} foreign intelligence agencies such as the \acs{CIA} or \acs{NSA} in the U.S.,
which are assumed to operate within---though push the boundaries of---the legal framework.)}

@@

Hawkish lawmakers threaten the security of a cryptosystem (whether it uses \ac{EA} or not) because they may judge the
system as too inhibitive to law enforcement. Therefore, they may outlaw its use and mandate something weaker in its
place.}
